
---
title: Interim Review
subtitle: Aaron Conway
author: Aaron Conway
date: "August 2021"
---

# CV 



```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results = "asis")
library(rorcid)
Sys.getenv("ORCID_TOKEN")
```



## Education {.break}
```{r  results='asis'}
targets::tar_load(edu)
glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{edu$title}</em><br>{edu$organization}<br>{edu$location} <span style="float:right;color:#929598;">{edu$time}</span>
           </li>
           </ul>')
```


## Employment
```{r}
targets::tar_load(employ)

glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{employ$title}</em><br>{employ$organization}<br>{employ$location} <span style="float:right;color:#929598;">{employ$time}</span>
           </li>
           </ul>')
```


## Awards {.break}

```{r}
targets::tar_load(distinctions)

glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{distinctions$title}</em><br>{distinctions$organization} <span style="float:right;color:#929598;">{distinctions$time}</span>
           </li>
           </ul>')
```


## Service {.break}

```{r}
targets::tar_load(service)
glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{service$title}</em><br>{service$organization} <span style="float:right;color:#929598;">{service$time}</span>
           </li>
           </ul>')
```


## Memberships

```{r}
targets::tar_load(membership)
glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{membership$title}</em><br>{membership$organization} <span style="float:right;color:#929598;">{membership$time}</span>
           </li>
           </ul>')
```


## Funding
```{r}
targets::tar_load(funding)


glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{funding$title}</em><br>{funding$funder}<br>{funding$Amount} <span style="float:right;color:#929598;">{funding$timeframe}</span>
           </li>
           </ul>')
```


## Publications

```{r}
targets::tar_load(papers)
targets::tar_load(articles)
targets::tar_load(editorials)
targets::tar_load(letters)
targets::tar_load(protocols)
targets::tar_load(preprints)
```

### Journal articles [`r nrow(articles)`]{.number}

<ul style="list-style-type:none;">
```{r articles}
glue::glue('
           <li>
           {articles$TITLE}
           <br>
           <em>{articles$JOURNAL}</em>
           <span style="float:right;color:#929598;">{articles$YEAR}</span>
           <br>
           <span class="authorBlock">{articles$authors}</span>
           </li>
           <hr>')
```

</ul>

### Editorials [`r nrow(editorials)`]{.number}

<ul style="list-style-type:none;">
```{r }
glue::glue('
           <li>
           {editorials$TITLE}
           <br>
           <em>{editorials$JOURNAL}</em>
           <span style="float:right;color:#929598;">{editorials$YEAR}</span>
           <br>
           <span class="authorBlock">{editorials$authors}</span>
           </li>
           <hr>')
```
</ul>

### Letters [`r nrow(letters)`]{.number}

<ul style="list-style-type:none;">
```{r }
glue::glue('
           <li>
           {letters$TITLE}
           <br>
           <em>{letters$JOURNAL}</em>
           <span style="float:right;color:#929598;">{letters$YEAR}</span>
           <br>
           <span class="authorBlock">{letters$authors}</span>
           </li>
           <hr>')
```
</ul>


### Protocols [`r nrow(protocols)`]{.number}

<ul style="list-style-type:none;">
```{r }
glue::glue('
           <li>
           {protocols$TITLE}
           <br>
           <em>{protocols$JOURNAL}</em>
           <span style="float:right;color:#929598;">{protocols$YEAR}</span>
           <br>
           <span class="authorBlock">{protocols$authors}</span>
           </li>
           <hr>')
```
</ul>

### Preprints [`r nrow(preprints)`]{.number}

<ul style="list-style-type:none;">
```{r }
glue::glue('
           <li>
           {preprints$TITLE}
           <br>
           <em>{preprints$JOURNAL}</em>
           <span style="float:right;color:#929598;">{preprints$YEAR}</span>
           <br>
           <span class="authorBlock">{preprints$authors}</span>
           </li>
           <hr>')
```
</ul>


### Book Chapters

<ul style="list-style-type:none;">
<li>
Common quantitative methods
<br>
<em>Nursing and Midwifery Research: Methods and Appraisal for Evidence Based Practice.[6th ed.]</em>
<span style="float:right;color:#929598;">2020</span>
<br>
<span class="authorBlock">
<strong>Aaron Conway</strong> | Jed Duff
</span>
</li>
<hr>
</ul>

## Software

```{r}
software <- tribble(
  ~package, ~description, ~year,
  "spiritR", "A workflow to enable direct upload of a clinical trial protocol to clinicaltrials.gov
", 2019
)

glue::glue('
  <ul style="list-style-type:none;">
  <li>
  <a href="https://spiritr.netlify.com"><em>{software$package}</em></a><br>{software$description} <span style="float:right;color:#929598;">{software$year}</span>
  </li>
  </ul>
  <hr>')
```

## Peer reviews
```{r}
targets::tar_load(reviews)

glue::glue('
<ul style="list-style-type:none;">
           <li>
           <em>{reviews$name}</em><span style="float:right;color:#929598;">{reviews$count}</span>
           </li>
           </ul>')
```

